### 2019-08-22 README.Rmd
attempt release of v2.4.0

- [A Brief Introduction to RNeXML](https://docs.ropensci.org/RNeXML/articles/intro)
- [RNeXML: A Package for Reading and Writing Richly Annotated Phylogenetic, Character, and Trait Data in R](https://docs.ropensci.org/RNeXML/articles/manuscript.pdf) (published in MEE).
- [Handling Metadata in RNeXML](https://docs.ropensci.org/RNeXML/articles/metadata)
- [The `nexml` S4 Object](https://docs.ropensci.org/RNeXML/articles/S4)
- [Semantic data & SPARQL with RNeXML](https://docs.ropensci.org/RNeXML/articles/sparql)
- [Extending NeXML: an example based on simmap](https://docs.ropensci.org/RNeXML/articles/simmap)

>>>>

- [A Brief Introduction to RNeXML](https://docs.ropensci.org/RNeXML/articles/intro)
- [RNeXML: A Package for Reading and Writing Richly Annotated Phylogenetic, Character, and Trait Data in R](https://github.com/ropensci/RNeXML/tree/master/manuscripts) (published in MEE).
- [Handling Metadata in RNeXML](https://docs.ropensci.org/RNeXML/articles/metadata)
- [The `nexml` S4 Object](https://docs.ropensci.org/RNeXML/articles/S4)
- [Semantic data & SPARQL with RNeXML](https://docs.ropensci.org/RNeXML/articles/sparql)
- [Extending NeXML: an example based on simmap](https://docs.ropensci.org/RNeXML/articles/simmap)
